Weakly Nonlinear MRI: Notes

### 2014-06-13 notes/mri_notes.tex
more notes
marginal solution
added marginal eigenfunctions
two attempts at AH solution -- figures
all positive L operators
red only figures

While this solution is symmetric about the origin, as expected, it does not have the same shape as the solution in Umurhan+.

>>>>

While this solution is symmetric about the origin, as expected, it does not have the same shape as the solution in Umurhan+. Note that the normalization is arbitrary. \\

We also use Dedalus to solve the linear MRI at marginality, that is, Umurhan+ Figure 2. Our solution, which agrees with theirs, is shown in Figure \ref{margsol}:

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{marginal_solution}
\caption{Marginal mode eigenfunctions.}
\label{margsol}
\end{figure*}

\pagebreak
The correct adjoint homogenous solution is still elusive. Here is everything I have tried so far. In what follows, red is the solution indicated in the title, and black is supposed to be zero everywhere. \\

1. $L = L_0 - L_1 dz + L_2 dz^2 - L_3 dz^3 + L_4 dz^4$ \\

Smallest eigenvalue: [-0.00624309 +1.97781664e-16j] \\

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{ah_attempt1}
\includegraphics[scale=0.5]{ah_attempt1_redonly}
\end{figure*}

\pagebreak
2. $L = L_0 + L_1 dz - L_2 dz^2 - L_3 dz^3 + L_4 dz^4$ \\

Smallest eigenvalue: [-0.00624309 +1.97781664e-16j] \\

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{ah_pmmp}
\includegraphics[scale=0.5]{ah_pmmp_redonly}
\end{figure*}

\pagebreak
3. $L = L_0 + L_1 dz + L_2 dz^2 + L_3 dz^3 + L_4 dz^4$ \\

Smallest eigenvalue: [-0.00624309 +1.97781664e-16j] \\

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{ah_allpos}
\includegraphics[scale=0.5]{ah_allpos_redonly}
\end{figure*}

\pagebreak
I also tried to solve the equations without any iQ's -- that is, without the $\partial_z$ terms: \\

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{ah_nodz}
\end{figure*}
